\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
    \usepackage{hyperref}
    \usepackage{fontawesome}
    \usepackage{helvet}
    \renewcommand{\familydefault}{\sfdefault}


    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}

	\textbf{{\Huge \scshape {Desmond Gilmour}}}\\
	\faPhone\space 519.546.9876 $|$ 
        \faEnvelope\space\href{mailto:desmondgilmour@gmail.com}{desmondgilmour@gmail.com} $|$  
        \faLinkedinSquare\space\href{https://www.linkedin.com/in/desmond-gilmour-886b3a128/}{@desmondgilmour} $|$
        \faGithubSquare\space\href{https://github.com/dessygil}{@dessygil}
        \\
\end{center}

%==== Summary ====%
\header {Summary}
I am an interdisciplinary researcher focused on the intersection of chemistry and computer science.
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{University of Guelph}\hfill Guelph, ON\\
Bachelor of Physical Sciences, Minor in Chemistry  \textit{GPA: 3.6} \hfill September 2016 - December 2021\\
Bachelor of Computer Science \textit{GPA: 3.6} \hfill September 2016 - December 2021\\
\vspace{2mm}

%=== Skills ===%
\header{Skills}
\begin{tabular}{ l l }
	Languages:        & Python, Java, C/C++, SQL, R                      \\
	Frameworks/Tools: & PyTorch, Pandas, Numpy, Git, Jupyter, Linux, RDKit, DeepChem \\
\end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Patsnap} \hfill WFH\\
\textit{Sales Development Representative} \hfill December 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Used cold outreach techniques to generate the highest amount of leads in Q3 (23) and the third highest revenue in Q2 (\$54,000) and Q3 (\$57,000).
	\item Successfully onboarded three new employees of various technical skills into a STEM-specific role, with two exceeding their sales target.
	\item Committed repetition, A/B testing, and coaching through over 25,000 cold calls and various cold outreach techniques.
\end{itemize}

\textbf{University of Guelph} \hfill Guelph, ON\\
\textit{NSERC Funded Research Assistant} \hfill May 2019 - September 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Synthesized a protected disaccharide acceptor (Lewis Y)          ready for glycosylation to a trisaccharide.
	\item Characterized all compounds in the synthetic scheme using        1D NMR, 2D NMR, Mass Spectrometry, and IR Spectroscopy.
        \item Reported, analyzed, and presented synthetic scheme at the CEPS undergraduate poster session to highlight protecting groups to be used towards Lewis Y.
\end{itemize}

\textit{Teaching Assistant} \hfill January 2019 - September 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Managed 60+ students per semester for first-year chemistry       W20 and second-year organic chemistry S20. 
        \item Mastered and taught students ChemDraw to communicate remotely and Gaussian to teach organic chemistry concepts during the pandemic.
	\item Received a TA rating of 4.8/5.0.
\end{itemize}

\textit{Residence Assistant} \hfill September 2018 - April 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Ensured the safety of 300+ Students.
	\item De-escalated dangerous situations and navigated                  disagreements between students.
        \item Planned events and built rapport with students to create an inclusive environment for all first-year students in South residence.
\end{itemize}

%==== Projects ====%

\header{Projects}

{\textbf{Quantification of Diastereomeric and Enantiomeric Mixtures of b-Aminoalkyl Sulfoxides Using ESI-FAIMS-MS}} \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Defended my fourth-year capstone project against a committee of three from the University of Guelph.
	\item Synthesized four B-Aminoalkyl Sulfoxides for comparison using ESI-FAIMS-MS.
\end{itemize}
\vspace*{1mm}

{\textbf{Bioactivity Prediction App for the target Protein-arginine deiminase type-4 (PADI4)}} {\sl Numpy, Pandas, RDKit, StreamLit, Lazy Predict, SKLearn} \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Produced an app that can predict the bioactivity of molecules inputted in SMILES format for the target PADI4.
	\item The machine learning model was trained using PubChem molecular fingerprints for data obtained from the ChEMBL Database.
\end{itemize}
\vspace*{1mm}

{\textbf{AlphaToe}} {\sl C}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed an unbeatable tic tac toe game that uses a pseudo artificial intelligence and runs in the terminal.
	\item A hashmap is used for possible moves, and each position is ranked to know which move to make next.\\
\end{itemize}
\vspace*{1mm}

{\textbf{Vintage Academy}} {\sl HTML, CSS, Shopify} \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Co-built a brand using Shopify that grossed approximately      \$2000/month.
	\item Manipulated frontend using UI/UX principles to streamline the buying process.\\
\end{itemize}

%=== Volunteer work ===%
\header{Volunteer Experience}

\textbf{University of Guelph} \hfill Guelph, ON\\
\textit{Auzanneau Group - Research Assistant} \hfill May 2019 - September 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Conducted research to develop tumor-associated carbohydrate antigens.
\end{itemize}

\textit{Chemistry Storage Facility - Front Desk Assistant} \hfill September 2019 - April 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Managed the distribution of deliveries, glassware, and chemicals to all biological and chemical research groups.
\end{itemize}

\textit{Dr. Stuttaford - Lab setup} \hfill September 2019 - April 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Set up reagents and machines to be used by students taking analytical chemistry 1.
\end{itemize}

\textit{Spriet Group - Research Assistant} \hfill September 2016 - April 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Conducted experiments with patients to measure their VO2 Max.
\end{itemize}

\textit{Biol*1080, Biol*1090 - Note Taker} \hfill September 2016 - April 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Offered my notes for students who could not take their own.
\end{itemize}


\end{document}